Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-02-17 WSSSPE2_report/WSSSPE2_review.tex
Appendix A: format.

@@

Jordan Adams          &  Tulane University                                                                    \\
Alice Allen           &  Astrophysics Source Code Library (ASCL)                                              \\
Gabrielle Allen       &  U Illinois                                                                           \\
Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA                                                                  \\
Wolfgang Bangerth     \\
David Bernholdt       &  Oak Ridge National Laboratory                                                        \\
Jakob Blomer          \\
Carl Boettiger        &  UCSC/ropensci                                                                        \\
Chris Bogart          &  ISR/CMU                                                                              \\
Steven R.~Brandt      &  Louisiana State University                                                           \\
Tom Clune             &  NASA GSFC                                                                            \\
John W.~Cobb          \\
Dirk Colbry           &  Michigan State University                                                            \\
Karen Cranston        &  NESCent                                                                              \\
Tom Crick             &  Cardiff Metropolitan University, UK                                                  \\
Ethan Davis           &  UCAR Unidata                                                                         \\
Robert R Downs        &  CIESIN, Columbia University                                                          \\
Anshu Dubey           &  Lawrence Berkeley National Laboratory                                                \\
Nicole Gasparini      &  Tulane University, New Orleans                                                       \\
Yolanda Gil           &  Information Sciences Institute, University of Southern California                    \\
Kurt Glaesemann       &  Pacific northwest national lab                                                       \\
Sol Greenspan         &  National Science Foundation                                                          \\
Ted Habermann         &  The HDF Group                                                                        \\
Marcus D.~Hanwell     &  Kitware                                                                              \\
Sarah Harris          &  University of Leeds                                                                  \\
David Henty           &  EPCC, The University of Edinburgh                                                    \\
Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh                         \\
James Howison         &  University of Texas                                                                  \\
Maxime Hughes         \\
Eric Hutton           &  University of Colorado                                                               \\
Ray Idaszak           &  RENCI/UNC                                                                            \\
Samin Ishtiaq         &  Microsoft Research Cambridge, UK                                                     \\
Matt Jones            &  University of California Santa Barbara                                               \\
Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland                          \\
Daniel S.~Katz        &  U Chicago \& Argonne                                                                 \\
Ian Kelley            \\
Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University                 \\
Chris Lenhardt        \\
Richard Littauer      &  MIT/University of Saarland                                                           \\
Frank L\"{o}ffler     &  Louisiana State University                                                           \\
Andre Luckow          &  Rutgers                                                                              \\
Berkin Malkoc         &  Istanbul Technical University                                                        \\
Kyle Marcus           &  University of Buffalo                                                                \\
Bryan Marker          &  The University of Texas at Austin                                                    \\
Suresh Marru          &  Indiana University                                                                   \\
Robert H.~McDonald    &  Indiana University - Data to Insight Center/Libraries                                \\
Rupert Nash           \\
Andy Nutter-Upham     &  Whitehead Institute                                                                  \\
Abani Patra           &  Univ @ Buffalo                                                                       \\
Aleksandra Pawlik     &  Software Sustainability Institute                                                    \\
Cody J.~Permann       &  Idaho National Laboratory                                                            \\
John W.~Peterson      &  Idaho National Laboratory                                                            \\
Benjamin Pharr        &  University of Mississippi                                                            \\
Stephen Piccolo       &  Brigham Young University, Utah                                                       \\
Marlon Pierce         &  Indiana University                                                                   \\
Ray Plante            &  NCSA/University of Illinois Urbana-Champaign                                         \\
Sushil Prasad         &  Georgia State University, Atlanta                                                    \\
Karthik Ram           &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci \\
Mike Rilee            &  NASA/GSFC, Rilee Systems Technologies                                                \\
Erin Robinson         &  Foundation for Earth Science                                                         \\
Mark Schildhauer      &  NCEAS, Univ. California, Santa Barbara                                               \\
Jory Schossau         &  Michigan State University                                                            \\
Frank Seinstra        &  Netherlands eScience Center                                                          \\
James Shepherd        &  Rice University                                                                      \\
Justin Shi            \\
Ardita Shkurti        &  University of Nottingham                                                             \\
Alan Simpson          &  EPCC, The University of Edinburgh                                                    \\
Carol Song            &  Purdue University                                                                    \\
James Spencer         &  Imperial College London                                                              \\
Tracy Teal            &  Data Carpentry                                                                       \\
Kaitlin Thaney        &  Mozilla Science Lab                                                                  \\
Matt Turk             &  NCSA/UIUC                                                                            \\
Colin C.~Venters      &  University of Huddersfield                                                           \\
Nathan Weeks          \\
Ethan White           &  University of Florida/Utah State University                                          \\
Nancy Wilkins-Diehr   &  SDSC                                                                                 \\
Greg Wilson           &  Software Carpentry                                                                   \\

@@

>>>>

{\small

@@

   Jordan Adams          &  Tulane University                                                                    
\\ Alice Allen           &  Astrophysics Source Code Library (ASCL)                                              
\\ Gabrielle Allen       &  U Illinois                                                                           
\\ Pierre-Yves Aquilanti &  TOTAL E\&P R\&T USA                                                                  
\\ Wolfgang Bangerth     
\\ David Bernholdt       &  Oak Ridge National Laboratory                                                        
\\ Jakob Blomer          
\\ Carl Boettiger        &  UCSC/ropensci                                                                        
\\ Chris Bogart          &  ISR/CMU                                                                              
\\ Steven R.~Brandt      &  Louisiana State University                                                           
\\ Tom Clune             &  NASA GSFC                                                                            
\\ John W.~Cobb          
\\ Dirk Colbry           &  Michigan State University                                                            
\\ Karen Cranston        &  NESCent                                                                              
\\ Tom Crick             &  Cardiff Metropolitan University, UK                                                  
\\ Ethan Davis           &  UCAR Unidata                                                                         
\\ Robert R Downs        &  CIESIN, Columbia University                                                          
\\ Anshu Dubey           &  Lawrence Berkeley National Laboratory                                                
\\ Nicole Gasparini      &  Tulane University, New Orleans                                                       
\\ Yolanda Gil           &  Information Sciences Institute, University of Southern California                    
\\ Kurt Glaesemann       &  Pacific northwest national lab                                                       
\\ Sol Greenspan         &  National Science Foundation                                                          
\\ Ted Habermann         &  The HDF Group                                                                        
\\ Marcus D.~Hanwell     &  Kitware                                                                              
\\ Sarah Harris          &  University of Leeds                                                                  
\\ David Henty           &  EPCC, The University of Edinburgh                                                    
\\ Neil Chue Hong        &  Software Sustainability Institute \& University of Edinburgh                         
\\ James Howison         &  University of Texas                                                                  
\\ Maxime Hughes         
\\ Eric Hutton           &  University of Colorado                                                               
\\ Ray Idaszak           &  RENCI/UNC                                                                            
\\ Samin Ishtiaq         &  Microsoft Research Cambridge, UK                                                     
\\ Matt Jones            &  University of California Santa Barbara                                               
\\ Nick Jones            &  New Zealand eScience Infrastructure, University of Auckland                          
\\ Daniel S.~Katz        &  U Chicago \& Argonne                                                                 
\\ Ian Kelley            
\\ Hilmar Lapp           &  National Evolutionary Synthesis Center (NESCent) and Duke University                 
\\ Chris Lenhardt        
\\ Richard Littauer      &  MIT/University of Saarland                                                           
\\ Frank L\"{o}ffler     &  Louisiana State University                                                           
\\ Andre Luckow          &  Rutgers                                                                              
\\ Berkin Malkoc         &  Istanbul Technical University                                                        
\\ Kyle Marcus           &  University of Buffalo                                                                
\\ Bryan Marker          &  The University of Texas at Austin                                                    
\\ Suresh Marru          &  Indiana University                                                                   
\\ Robert H.~McDonald    &  Indiana University - Data to Insight Center/Libraries                                
\\ Rupert Nash           
\\ Andy Nutter-Upham     &  Whitehead Institute                                                                  
\\ Abani Patra           &  Univ @ Buffalo                                                                       
\\ Aleksandra Pawlik     &  Software Sustainability Institute                                                    
\\ Cody J.~Permann       &  Idaho National Laboratory                                                            
\\ John W.~Peterson      &  Idaho National Laboratory                                                            
\\ Benjamin Pharr        &  University of Mississippi                                                            
\\ Stephen Piccolo       &  Brigham Young University, Utah                                                       
\\ Marlon Pierce         &  Indiana University                                                                   
\\ Ray Plante            &  NCSA/University of Illinois Urbana-Champaign                                         
\\ Sushil Prasad         &  Georgia State University, Atlanta                                                    
\\ Karthik Ram           &  University of California, Berkeley. Berkeley Institute for Data Science and rOpenSci 
\\ Mike Rilee            &  NASA/GSFC, Rilee Systems Technologies                                                
\\ Erin Robinson         &  Foundation for Earth Science                                                         
\\ Mark Schildhauer      &  NCEAS, Univ. California, Santa Barbara                                               
\\ Jory Schossau         &  Michigan State University                                                            
\\ Frank Seinstra        &  Netherlands eScience Center                                                          
\\ James Shepherd        &  Rice University                                                                      
\\ Justin Shi            
\\ Ardita Shkurti        &  University of Nottingham                                                             
\\ Alan Simpson          &  EPCC, The University of Edinburgh                                                    
\\ Carol Song            &  Purdue University                                                                    
\\ James Spencer         &  Imperial College London                                                              
\\ Tracy Teal            &  Data Carpentry                                                                       
\\ Kaitlin Thaney        &  Mozilla Science Lab                                                                  
\\ Matt Turk             &  NCSA/UIUC                                                                            
\\ Colin C.~Venters      &  University of Huddersfield                                                           
\\ Nathan Weeks          
\\ Ethan White           &  University of Florida/Utah State University                                          
\\ Nancy Wilkins-Diehr   &  SDSC                                                                                 
\\ Greg Wilson           &  Software Carpentry                                                                   

@@

}
